MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-11-14 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\subsection{The Join Challenge}\label{s:tjc}
Sometimes, web services can increase their overall utility by collaborating with other web services as communities. This collaboration helps them with better ways of sharing resources, higher reputation, better market share and wider visibility. Web services and communities come with different internal and external parameters and long-term outcome is dependent on these parameters.

The goal of all parties involved in the community is to maximize their long-term outcome while they are operating as part of the community. Web services need to be utilized with a selection strategy to choose from all the different possible collaboration groups they can form and also an estimation method for evaluating the long-term gain of joining different possible communities. Web services need to experiment different possible collaborative groups with other web services in order to estimate their gain over time. However, with high number of possible communities and many other business restrictions its not possible to test run collaboration with random web services. Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of possible number of partition of web services into communities, would make any brute-force type algorithm for best community selection strategy intractable and non-practical in real-world application settings.

\subsection{Join Consequences}\label{s:jc}
It is worth mentioning that a join event takes place as a result of two parties that are looking for expanding their collaborations. All actions are picked in attempt to enhance the overall outcome. However, the selected action may result in decreasing the overall utility in long term. This is the case where a single web service joins a community, but the complex process of task allocation eliminates the visibility of the web service and thus, the web service stays idle within the community. In other words the join action is not beneficial for the web service and in the first spot, it was a bad decision.  The same event might be beneficial for the community as it hosts a web service that in case of a relative task can engage the web service in the task. But overall, both sides do not benefit from collaborating with each other and the join event has negative consequences in at least one sides' utility.

>>>>

\subsection{The Join Challenge}\label{s:tjc}
Sometimes, web services can increase their overall utility by collaborating with other web services as communities. This collaboration helps them with better ways of sharing resources, higher reputation, better market share and wider visibility. Web services and communities come with different internal and external parameters, and the long-term outcome is dependent on these parameters.

The goal of all parties involved in the community is to maximize their long-term outcome while they are operating as part of the community. Web services need to be utilized with a selection strategy to choose from all of the different possible collaboration groups they can form as well as an estimation method for evaluating the long-term gain of joining different possible communities. Web services need to experiment with different possible collaborative groups and other web services in order to estimate their gain over time. However, with a high number of possible communities and many other business restrictions, it is not possible to test run collaboration with random web services. Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of the possible number of partitions of web services into communities, would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.

\subsection{Join Consequences}\label{s:jc}
It is worth mentioning that a \emph{join} event takes place as a result of two parties that are looking for expanding their collaborations. All actions are picked in attempt to enhance the overall outcome. However, the selected action may result in decreasing the overall utility in long term. This is the case where a single web service joins a community, but the complex process of task allocation eliminates the visibility of the web service and thus, the web service stays idle within the community. In other words the join action is not beneficial for the web service and in the first spot, it was a bad decision.  The same event might be beneficial for the community as it hosts a web service that in case of a relative task can engage the web service in the task. But overall, both sides do not benefit from collaborating with each other and the join event has negative consequences in at least one sides' utility.
